Brownian Dynein Model

### 2015-07-23 latex/derivation.tex
Add simplified angular velocity equations.

\section{Solution for $\dot{\Theta_{br}}$}

@@

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\tan(\Theta_{br}-\pi) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\tan^{-1}(\Theta_{br}-\pi)}
\end{equation}

\section{Solution for $\dot{\Theta_{mr}}$}

@@

\begin{multline}
\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) = \\
\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
+ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
\end{multline}

\begin{multline}
L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) \\
+ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) 
- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}}
{L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} + L_{s}\cos(\Theta_{mr}-\pi)} \\
  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr}}
  {L_{s}\sin(\Theta_{mr}-\pi) + L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}}
\end{multline}

@@

@@

>>>>

\section{Solution for $\dot{\Theta}_{br}$}

@@

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
{\Big (\frac{{L_{t}}^2\sin^2(\Theta_{br}-\pi)}{L_{t}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{t}}^2\cos^2(\Theta_{br}-\pi)}{L_{t}\sin(\Theta_{br}-\pi)} \Big) }
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
{\Big( {L_{t}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
{\Big ({L_{t}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big) }
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
{{L_{t}}^2}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
{{L_{t}}^2}
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
+ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{equation}

\section{Solution for $\dot{\Theta}_{mr}$}

@@

\begin{multline}
\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t }) = \\
\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
+ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t })
\end{multline}

\begin{multline}
L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) =
\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) \\
+ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t }) 
- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t })
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (X_{mr} - X_{t })}
{L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t}) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })} \\
  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(Y_{mr} - Y_{t })}
  {L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })}
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
{L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))} \\
  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
  {L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))}
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
{{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)} \\
  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
  {{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)}
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big) (L_{s}\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{ml} = \\
\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)} \\
- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)}
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} = \\
\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
{{L_s}^2} \\
- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
{{L_s}^2}
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} = \\
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big( \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+ \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big( \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+ \dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big( L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+ \dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
